Derive final annotations based on NBAtlas reference

### 2025-08-14 analyses/cell-type-neuroblastoma-04/final-annotation.Rmd
aha, wrong palette file name
Ok, I had a palette bug

# palette file
palette_file <- file.path(
  module_dir,
  "palettes",
  "submission-palette.tsv"
)

@@

```{r}
# Finalize the annotations
submission_df <- annotation_df |>
  # add ontology ids
  dplyr::left_join(
    nbatlas_ontology_ids, 
    by = c("cell_type_assignment" = "NBAtlas_label")
  ) |>
  # recode labels
  dplyr::mutate(
    cell_type_assignment = dplyr::case_when(
      is.na(cell_type_assignment) ~ "Unknown", 
      cell_type_assignment == "NE" ~ "Neuroendocrine/tumor",
      .default = cell_type_assignment
   ),
    tumor_cell_classification = dplyr::case_when(
      cell_type_assignment == "Unknown" ~ "Unknown", 
      cell_type_assignment == "Neuroendocrine/tumor" ~ "tumor", 
      .default = "normal"
    )
  ) |>
  tidyr::separate(cell_id, into = c("library_id", "cell_barcode"), remove = FALSE) |>
  dplyr::select(
    cell_id, library_id, cell_barcode, cell_type_assignment, tumor_cell_classification, CL_ontology_id
  )
```

>>>>

# palette file
palette_file <- file.path(
  module_dir,
  "palettes",
  "nbatlas-cell-type-palette.tsv"
)

@@

```{r}
# Finalize the annotations
submission_df <- annotation_df |>
  # add ontology ids
  dplyr::left_join(
    nbatlas_ontology_ids, 
    by = c("cell_type_assignment" = "NBAtlas_label")
  ) |>
  # recode labels
  dplyr::mutate(
    cell_type_assignment = dplyr::case_when(
      is.na(cell_type_assignment) ~ "Unknown", 
      cell_type_assignment == "NE" ~ "Neuroendocrine/tumor",
      .default = cell_type_assignment
   ),
    tumor_cell_classification = dplyr::case_when(
      cell_type_assignment == "Unknown" ~ "Unknown", 
      cell_type_assignment == "Neuroendocrine/tumor" ~ "tumor", 
      .default = "normal"
    )
  ) |>
  tidyr::separate(cell_id, into = c("library_id", "cell_barcode"), remove = FALSE) |>
  dplyr::select(
    cell_id, library_id, cell_barcode, cell_type_assignment, tumor_cell_classification, CL_ontology_id
  )
# update palette label as well
names(celltype_pal)[names(celltype_pal) == "Neuroendocrine"] <- "Neuroendocrine/tumor"
```
